Draft: Notes on the revised Hidden weight function

### 2024-09-23 RevisedHiddenWeight.tex

Another immediate case for zero coefficients is the following:
\begin{Prop}
    If $p=q$ and $k$ is odd, then $\Dnka nka=0=\Dnka n{n-k}a$.
\end{Prop}

@@

\begin{remark}
    There are still instances where $\Dnka nka=0$ which have not been described by the above. For instance, we have $\Dnka{34}4a=0$ if $\{p,q\}=\{1,2\}$.
\end{remark}

@@

\begin{Prop}\mbox{}
    \begin{enumerate}
        \item The sum and alternating sum over $k$ of the $\Dnka nka$ are, respectively:
        \begin{gather*}
            \sum_{k=0}^n\Dnka nka=(-1)^{q}2^{n/2},\\
            \sum_{k=0}^n(-1)^k\Dnka nka=(-1)^{p}2^{n/2}.
        \end{gather*}
        \item The sum over the even and the odd $k$ of the the $\Dnka nka$ are, respectively:
        \begin{gather*}
            \sum_{k=0}^{n/2}\Dnka n{2k}a=2^{n/2-1}\big((-1)^{q}+(-1)^{p}\big),\\
            \sum_{k=0}^{n/2-1}\Dnka n{2k+1}a=2^{n/2-1}\big((-1)^{q}-(-1)^{p}\big).
        \end{gather*}
    \end{enumerate}
\end{Prop}

@@

\begin{table}
    \centering
    \begin{tabular}{|c|c|c|}
    \hline
    $n$ & $\max_{a\in\F_2^n}|W_f(a)|$ & $B_n$ \\ \hline
    $2$  & $2$     & $2$     \\
    $4$  & $8$     & $8$     \\
    $6$  & $20$    & $28$    \\
    $8$  & $52$    & $76$    \\
    $10$ & $108$   & $212$   \\
    $12$ & $292$   & $596$   \\
    $14$ & $700$   & $1\,828$  \\
    $16$ & $2\,176$  & $5\,196$  \\
    $18$ & $4\,964$  & $14\,668$  \\
    $20$ & $14\,032$ & $41\,468$ \\
    $22$ & $34\,232$ & $118\,544$ \\
    $24$ & $109\,648$ & $325\,188$ \\ \hline
    \end{tabular}
    \caption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ vs.\ our bound $B_n$}
    \label{table:max_walsh_vs_bound}
\end{table}

\begin{table}
    \centering
    \begin{minipage}{0.19\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $B_n$ \\
            \hline
            $2$  & $2.00 \cdot 10^{0}$  \\
            $4$  & $8.00 \cdot 10^{0}$  \\
            $6$  & $2.80 \cdot 10^{1}$  \\
            $8$  & $7.60 \cdot 10^{1}$  \\
            $10$ & $2.12 \cdot 10^{2}$ \\
            $12$ & $5.96 \cdot 10^{2}$ \\
            $14$ & $1.83 \cdot 10^{3}$ \\
            $16$ & $5.20 \cdot 10^{3}$ \\
            $18$ & $1.47 \cdot 10^{4}$ \\
            $20$ & $4.15 \cdot 10^{4}$ \\
            \hline
        \end{tabular}
    \end{minipage}%
    \begin{minipage}{0.19\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $B_n$ \\
            \hline
            $22$ & $1.19 \cdot 10^{5}$ \\
            $24$ & $3.25 \cdot 10^{5}$ \\
            $26$ & $9.59 \cdot 10^{5}$ \\
            $28$ & $2.68 \cdot 10^{6}$ \\
            $30$ & $7.65 \cdot 10^{6}$ \\
            $32$ & $2.14 \cdot 10^{7}$ \\
            $34$ & $6.25 \cdot 10^{7}$ \\
            $36$ & $1.76 \cdot 10^{8}$ \\
            $38$ & $5.03 \cdot 10^{8}$ \\
            $40$ & $1.40 \cdot 10^{9}$ \\
            \hline
        \end{tabular}
    \end{minipage}%
    \begin{minipage}{0.19\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $B_n$ \\
            \hline
            $42$ & $4.01 \cdot 10^{9}$ \\
            $44$ & $1.12 \cdot 10^{10}$ \\
            $46$ & $3.21 \cdot 10^{10}$ \\
            $48$ & $8.91 \cdot 10^{10}$ \\
            $50$ & $2.56 \cdot 10^{11}$ \\
            $52$ & $7.12 \cdot 10^{11}$ \\
            $54$ & $2.05 \cdot 10^{12}$ \\
            $56$ & $5.73 \cdot 10^{12}$ \\
            $58$ & $1.65 \cdot 10^{13}$ \\
            $60$ & $4.59 \cdot 10^{13}$ \\
            \hline
        \end{tabular}
    \end{minipage}%
    \begin{minipage}{0.19\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $B_n$ \\
            \hline
            $62$ & $1.32 \cdot 10^{14}$ \\
            $64$ & $3.66 \cdot 10^{14}$ \\
            $66$ & $1.05 \cdot 10^{15}$ \\
            $68$ & $2.93 \cdot 10^{15}$ \\
            $70$ & $8.40 \cdot 10^{15}$ \\
            $72$ & $2.33 \cdot 10^{16}$ \\
            $74$ & $6.71 \cdot 10^{16}$ \\
            $76$ & $1.87 \cdot 10^{17}$ \\
            $78$ & $5.39 \cdot 10^{17}$ \\
            $80$ & $1.51 \cdot 10^{18}$ \\
            \hline
        \end{tabular}
    \end{minipage}
    \caption{Values of $B_n$ for various $n$.}
    \label{table:walsh_bounds}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=10cm]{walsh_bound}
    \caption{Our bounds $B_n$ in terms of $n$, on a logarithmic scale}
    \label{fig:walsh_bound}
\end{figure}
\newpage

>>>>

Another immediate case for zero coefficients is the following:
\begin{Prop}

    If $p=q$ and $k$ is odd, then $\Dnka nka=0=\Dnka n{n-k}a$.
\end{Prop}

@@

\begin{remark}
    There are still instances where $\Dnka nka=0$ which have not been described by the above. For instance, we have $\Dnka{34}4a=0$ if $\{p,q\}=\{1,2\}$.
\end{remark}
>>>>>>> 927bf10bd354d63e33833a2cff7df1af6d3d3523

@@

\begin{Prop}\mbox{}
    \begin{enumerate}
        \item The sum and alternating sum over $k$ of the $\Dnka nka$ are, respectively:
        \begin{gather*}
            \sum_{k=0}^n\Dnka nka=(-1)^{q}2^{n/2},\\
            \sum_{k=0}^n(-1)^k\Dnka nka=(-1)^{p}2^{n/2}.
        \end{gather*}
        \item The sum over the even and the odd $k$ of the the $\Dnka nka$ are, respectively:
        \begin{gather*}
            \sum_{k=0}^{n/2}\Dnka n{2k}a=2^{n/2-1}\big((-1)^{q}+(-1)^{p}\big),\\
            \sum_{k=0}^{n/2-1}\Dnka n{2k+1}a=2^{n/2-1}\big((-1)^{q}-(-1)^{p}\big).
        \end{gather*}
    \end{enumerate}

\end{Prop}

@@

\begin{table}
    \centering
    \begin{tabular}{|c|c|c|}
    \hline
    $n$ & $\max_{a\in\F_2^n}|W_f(a)|$ & $B_n$ \\ \hline
    $2$  & $2$     & $4$     \\
    $4$  & $8$     & $14$     \\
    $6$  & $20$    & $36$    \\
    $8$  & $52$    & $114$    \\
    $10$ & $108$   & $288$   \\
    $12$ & $292$   & $820$   \\
    $14$ & $700$   & $2\,316$  \\
    $16$ & $2\,176$  & $6\,006$  \\
    $18$ & $4\,964$  & $18\,192$  \\
    $20$ & $14\,968$ & $48\,480$ \\
    $22$ & $34\,232$ & $140\,392$ \\
    $24$ & $109\,648$ & $392\,168$ \\ \hline
    \end{tabular}
    \caption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ vs.\ our bound $B_n$}
    \label{table:max_walsh_vs_bound}
\end{table}

Here is the updated table with the new values for \( B_n \) corresponding to each \( n \):

\begin{table}
    \centering
    \begin{minipage}{0.24\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $B_n$ \\
            \hline
            $2$  & $4.00 \cdot 10^{0}$  \\
            $4$  & $1.40 \cdot 10^{1}$  \\
            $6$  & $3.60 \cdot 10^{1}$  \\
            $8$  & $1.14 \cdot 10^{2}$  \\
            $10$ & $2.88 \cdot 10^{2}$  \\
            $12$ & $8.20 \cdot 10^{2}$  \\
            $14$ & $2.32 \cdot 10^{3}$  \\
            $16$ & $6.01 \cdot 10^{3}$  \\
            $18$ & $1.82 \cdot 10^{4}$  \\
            $20$ & $4.85 \cdot 10^{4}$  \\
            \hline
        \end{tabular}
    \end{minipage}%
    \begin{minipage}{0.24\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $B_n$ \\
            \hline
            $22$ & $1.40 \cdot 10^{5}$  \\
            $24$ & $3.92 \cdot 10^{5}$  \\
            $26$ & $1.14 \cdot 10^{6}$  \\
            $28$ & $3.12 \cdot 10^{6}$  \\
            $30$ & $8.90 \cdot 10^{6}$  \\
            $32$ & $2.50 \cdot 10^{7}$  \\
            $34$ & $7.14 \cdot 10^{7}$  \\
            $36$ & $2.04 \cdot 10^{8}$  \\
            $38$ & $5.75 \cdot 10^{8}$  \\
            $40$ & $1.62 \cdot 10^{9}$  \\
            \hline
        \end{tabular}
    \end{minipage}%
    \begin{minipage}{0.24\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $B_n$ \\
            \hline
            $42$ & $4.59 \cdot 10^{9}$  \\
            $44$ & $1.29 \cdot 10^{10}$ \\
            $46$ & $3.63 \cdot 10^{10}$ \\
            $48$ & $1.02 \cdot 10^{11}$ \\
            $50$ & $2.88 \cdot 10^{11}$ \\
            $52$ & $8.06 \cdot 10^{11}$ \\
            $54$ & $2.30 \cdot 10^{12}$ \\
            $56$ & $6.45 \cdot 10^{12}$ \\
            $58$ & $1.83 \cdot 10^{13}$ \\
            $60$ & $5.14 \cdot 10^{13}$ \\
            \hline
        \end{tabular}
    \end{minipage}%
    \begin{minipage}{0.24\textwidth}
        \centering
        \begin{tabular}{|c|c|}
            \hline
            $n$ & $B_n$ \\
            \hline
            $62$ & $1.47 \cdot 10^{14}$ \\
            $64$ & $4.09 \cdot 10^{14}$ \\
            $66$ & $1.17 \cdot 10^{15}$ \\
            $68$ & $3.25 \cdot 10^{15}$ \\
            $70$ & $9.34 \cdot 10^{15}$ \\
            $72$ & $2.60 \cdot 10^{16}$ \\
            $74$ & $7.44 \cdot 10^{16}$ \\
            $76$ & $2.08 \cdot 10^{17}$ \\
            $78$ & $5.97 \cdot 10^{17}$ \\
            $80$ & $1.65 \cdot 10^{18}$ \\
            \hline
        \end{tabular}
    \end{minipage}
    \caption{Values of $B_n$ for various $n$}
    \label{table:walsh_bounds}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=10cm]{walsh_bound}
    \caption{Our bounds $B_n$ in terms of $n$, on a logarithmic scale}
    \label{fig:walsh_bound}
\end{figure}

\pmnote{Bounds on Dnk from complex analysis}

\pmnote{practical experiments for the function.}

\subsection{Generalization}

\begin{definition}
	Let $n\in \N$ be an even number and $t \in \N $ no greater than $n/2$, we denote by $d_{t,n}$ the function given by: $d_{t,n}(x)=\sum_{i=1}^t x_{2i-1} x_{2i}$.

	%	by $\Dnka{n}{k}{a}$:
	%	\[\Dnka{n}{k}{a}= \sum_{x\in \Ekn{k}{n}} (-1)^{d_n(x) +a x}\]
\end{definition}

In particular, $d_{n,n}(x)=d_n(x)$.

We focus on the Walsh spectrum restricted to the slices of any function $d_{t,n}$

\begin{proposition}\label{prop:dtn}
	Let $t, n\in \N$ with $n$ even and $t\le n/2$, the following holds on $d_{t,n}$ for all $k\in [0,n]$:
	\[\wtk{d_{t,n}}{k}(a)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t},\]
	where $b$ denotes the first $2t$ elements of $a$ and $c$ the last $n-2t$ elements.

\end{proposition}
\begin{proof}
	We rewrite the restricted Walsh transform, denoting $x\in \F_2^n$ by $(y,z)$ where $y\in \F_2^{2t}$ and $z \in \F_2^{n-2t}$, and similarly denoting $a$ by $(b,c)$:

	\begin{align*}
	\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,t}(y)+by +cz}\\
	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t} \atop z \in \Ekn{k-\ell}{n-2t}} (-1)^{d_{t,t}(y)+by +cz}\\
	&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,t}(y)+by} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{cz}\right)\\
	&=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.
	\end{align*}

\end{proof}

\newpage
